\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-09-11 paper.tex
Add citation and rewording

\section{\normalsize\textbf{Related Work}}
The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and blockchain is considered a solution.

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract and Cloud Server. Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization. However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers. Also, the performance analysis shows that IoT devices have low efficiency interacting with Etheruem due to the time-consuming Proof-of-Work(PoW) process.

@@

On the basis of the Tangle and MAM, IOTA foundation proposed a decentralized Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM. Nevertheless, the platform design is centralized, new devices require manual approval from IOTA team to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker. Where broker is a highly resourced and trustless device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant are still future work.

@@

The previous work proposed different solution to specific issues of data marketplace. In this paper, we proposed an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subsciption on distributed ledger.

@@

\subsection{Components}
\subsubsection{Masked Authenticated Messaging}
IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency while MAM is the second layer data communication protocol built on top of Tangle.

MAM resolves the challenge to publish encrypted streaming data to distributed ledgers. It publishes messages encrypted with a \textbf{session key} to \textbf{channel}, which is a form of transactions that each address can be derived from the previous one. Therefore, with \textbf{channel root}, the first message of a channel, and the session key, all data on the channel is accessible.

One can create multiple channels as possible, however, the size of a channel is fixed which is decided before creation, thus data providers should decide how to distribute data product into MAM channels. While the creation of a MAM channel is time-consuming, brokers are also responsible for channel creation, encrypted data publishing and session key certification in our system. See Figure \ref{fig:launching_product}

@@

\subsubsection{Ethereum Smart Contract}
Smart contract\cite{smartContract} is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.

>>>>

\section{\normalsize\textbf{Related Work}}
The economic value of huge amount of data emerges, several researchers have started to explore the design of data marketplace. The Third Party Auditors (TPAs)-based frameworks\cite{TPA} is far from being satisfactory due to the unstandardize data format and dynamic nature of IoT data. Therefore a decentralized data integrity validation and trading process has been proposed recent years, and blockchain is considered a solution.

Data Integrity as a Service (DIaaS) is a blockchain based framework for data integrity proposed by Liu et al.\cite{DIaas} which is a Cloud Server Service (CSS) allows both data provider and consumer to validate data integrity by comparing hashes on Ethereum smart contract\cite{smartContract} and Cloud Server. Moreover, Ethereum smart contract can also realize the purchase agreement, including authoriziation and the penalization. However, the architecture of DIaaS needs highly trust on CSS, if CSS is malicious or crashed, that will cause losses to both providers and consumers. Also, the performance analysis shows that IoT devices have low efficiency interacting with Ethereum due to the time-consuming Proof-of-Work(PoW) process.

@@

On the basis of the Tangle and MAM, IOTA foundation launched a Data Marketplace\cite{IOTADataMarket} which is suitable for IoT streaming data that not only allows data providers to put data on Tangle without any trusted cloud services, but also allow providers and consumers to trade on Tangle and protect privacy and assure data integrity from source with MAM. Nevertheless, the platform design is centralized, new devices require manual approval from IOTA foundation to be visible in the marketplace. Also, interacting with Tangle is still the bottleneck for low-level devices especially in an unstable network or electricity environment.

A different framework design proposed by Gupta, S.Kanhere and Jurdak\cite{3tierDataMarket} could reduce the burden of low-level devices as mentioned. The infrastructure is a 3-tier decentralized data marketplace architectural design with Ethereum smart contract which consists of provider, consumer and broker. Where broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant are still future work.

@@

The previous work proposed different solution to specific issues of data marketplace. In this paper, we had an  overall design of decentralized data marketplace that takes care of data integrity and trading procedure such as buyout and subscibing to future data on distributed ledger.

@@

\subsection{Component}
\subsubsection{Masked Authenticated Messaging}
IOTA\cite{IOTAwhitepaper} is a feeless and scalable cryptocurrency for the IoT industry based on a the distributed  ledger consists of a directed acyclic graph(DAG) of individual transactions, \textbf{Tangle}. The innovative consensus algorithm allows people to make \textbf{zero-transactions} that one could store information securely within Tangle transactions. Nevertheless, publishing encrypted streaming data to distributed ledgers is still a challenge, which one need to keep the address and session key per message, otherwise attackers could easily issue spam transactions if publishing with the same address.

However, MAM resolves this problem, it is a second layer data communication protocol enables to emit and access an encrypted data stream over Tangle network and ensures data integrity.
It publishes each message to different addresses that each can be derived from the previous one, this forms a MAM channel. Furthermore, a session key can be provided to control the visibility and access to a MAM channel.

@@

\subsubsection{Ethereum Smart Contract}
Smart contract is a protocol for formulating agreement on blockchain that provides verification and execution of the contract. The code in the smart contract could interact with other contracts, make decisions, store data and transfer cryptocurrency. All conditions and states established in the contract are transparent and with enforcement. The appearance of smart contracts makes trading more flexible, and achieves more complex trading patterns in reality.
